KidsAIR: exposure model

### 2020-04-13 ambient_summary.Rmd
update file path method/backup

---
title: "KidsAIR: ambient temperature and PM analysis"
author: "Ethan Walker"
date: "Started 1 April 2020, Updated 3 April 2020"
output: pdf_document
---

@@

```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long_new.rds")

exposure_analysis_data_medium <- read_rds("Output/exposure_analysis_data_medium.rds")

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds")

sums_rolling_pm_data <- read_rds("Output/sums_rolling_pm_data.rds")

health_exposure_data_sampling_day <- read_rds("Output/health_exposure_data_sampling_day.rds")
```

>>>>

---
title: "KidsAIR: ambient temperature and PM analysis"
author: "Ethan Walker"
date: "Started 1 April 2020, Updated 13 April 2020"
output: pdf_document
---

@@

```{r}
input_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/Input/")
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
input_file <- c("exposure_analysis_data_long_new.rds")
output_file <- c("exposure_analysis_data_long_new.rds")

exposure_analysis_data_long <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_long_new.rds"))

exposure_analysis_data_medium <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_medium.rds"))

exposure_analysis_data_short <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_short.rds"))

sums_rolling_pm_data <- 
  read_rds(paste0(output_path, "Output/sums_rolling_pm_data.rds"))

health_exposure_data_sampling_day <- 
  read_rds(paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))
```

### 2020-04-13 exposure_initial_analysis.Rmd
update file path method/backup

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 9 April 2020"
output: pdf_document
---

@@

# Load individual datasets
```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long_new.rds")

exposure_analysis_data_medium <- read_rds("Output/exposure_analysis_data_medium.rds")

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds")

sums_rolling_pm_data <- read_rds("Output/sums_rolling_pm_data.rds")

health_exposure_data_sampling_day <- read_rds("Output/health_exposure_data_sampling_day.rds")
```

>>>>

---
title: "KidsAIR: initial exposure analysis"
author: "Ethan Walker"
date: "Started 2 Feb 2020, Updated 13 April 2020"
output: pdf_document
---

@@

# Load individual datasets
```{r}
input_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/Input/")
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
input_file <- c("exposure_analysis_data_long_new.rds")
output_file <- c("exposure_analysis_data_long_new.rds")

exposure_analysis_data_long <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_long_new.rds"))

exposure_analysis_data_medium <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_medium.rds"))

exposure_analysis_data_short <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_short.rds"))

sums_rolling_pm_data <- 
  read_rds(paste0(output_path, "Output/sums_rolling_pm_data.rds"))

health_exposure_data_sampling_day <- 
  read_rds(paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))
```

### 2020-04-13 exposure_models.Rmd
update file path method/backup

---
title: "KidsAIR: exposure model"
author: "Ethan Walker"
date: "Started 19 March 2020, Updated 20 March 2020"
output: pdf_document
---

@@

```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long.rds")

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds") 
```

>>>>

---
title: "KidsAIR: exposure model"
author: "Ethan Walker"
date: "Started 19 March 2020, Updated 13 April 2020"
output: pdf_document
---

@@

```{r}
input_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/Input/")
output_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
input_file <- c("exposure_analysis_data_long_new.rds")
output_file <- c("exposure_analysis_data_long_new.rds")

exposure_analysis_data_long <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_long_new.rds"))

exposure_analysis_data_medium <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_medium.rds"))

exposure_analysis_data_short <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_short.rds"))

sums_rolling_pm_data <- 
  read_rds(paste0(output_path, "Output/sums_rolling_pm_data.rds"))

health_exposure_data_sampling_day <- 
  read_rds(paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))
```
